%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{quentin}{bahers}
       {software engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Chiswick, W4
    London
    UK
    ~
    +44 7939 045112
    \href{mailto:quentin.bahers@gmail.com}{quentin.bahers@gmail.com}
    \href{http://github.com/qbahers}{github.com/qbahers}
    \href{http://twitter.com/qbahers}{twitter.com/qbahers}
  \section{languages}
    bilingual French/English
    Japanese \& Chinese notions
  \section{programming}
    {\color{red} $\varheartsuit$} JavaScript
    (Node.js, AngularJS)
    Ruby, Rails
    Java, Scala
\end{aside}

%\section{interests}

%complex networks, social networks, community detection, community structure,
%overlapping communities, information diffusion, viral marketing, social
%inference, recommendation, data mining

\section{education}

\begin{entrylist}
  \entry
    {2013–2014}
    {MSc in Computer Science}
    {Uppsala University, Sweden}
    {Uppsala University ranks among the best universities in Northern Europe}
  \entry
    {2010–2014}
    {MSc in Telecommunications}
    {Télécom Bretagne, France}
    {Télécom Bretagne is one of the most selective graduate schools in France}
  \entry
    {2011}
    {Student Exchange Program}
    {The University of Hong Kong, China}
    {Courses in Computer Science, Economics, Management and Chinese}
  \entry
    {2007–2010}
    {Classes Préparatoires aux Grandes Écoles}
    {Lycée Chateaubriand, France}
    {Intensive courses in Mathematics and Physics to prepare for the highly selective entrance exams to the French "Grandes Écoles".
    \\ Equivalent to a BSc in Mathematics and Physics}
  \entry
    {2007}
    {High School Diploma with Highest Honors}
    {Lycée Félix le Dantec, France}
    {}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {since 2015}
    {Software Engineer, Orange}
    {London, United Kingdom}
    {Working on the Libon web client. Libon is a service providing VoIP, instant messaging, and visual voicemail.
    \emph{Technologies: Backbone.js, XMPP}}
  \entry
    {04–10 2014}
    {Master Thesis, Ericsson}
    {Stockholm, Sweden}
    {AI Planning-Based Service Modeling for the Internet of Things}
  \entry
    {2012–2013}
    {Software Engineer Intern, Orange}
    {Tokyo, Japan}
    {- Co-developed a content delivery solution using next-generation WiFi 
    (backend, frontend \& Windows Store app).
    \emph{Technologies: Ruby on Rails, Scala, C\#}
    \\
    - Prototyped (from idea to proof of concept) an analytics tool for shop fronts using face tracking with a Kinect. 
    \emph{Technologies: Microsoft Kinect SDK, D3.js}}
\end{entrylist}

\section{applications}

\begin{entrylist}
  \entry
    {2015}
    {AleaBeat}
    {\href{http://git.io/vvLH5}{git.io/vvLH5}}
    {A web application to discover new music in a collaborative way.
    \\ \emph{Technologies: Node.js, AngularJS, MongoDB, SoundCloud SDK}}
  \entry
    {2014–2015}
    {Competitive Programming}
    {\href{http://git.io/vvLHu}{git.io/vvLHu}}
    {Solved over 200 algorithmic challenges on TopCoder and Google Code Jam.
    \\ \emph{Technologies: Java, Ruby}}
  \entry
    {2014}
    {Personal Website}
    {\href{http://qbahers.github.io}{qbahers.github.io}}
    {Developed my personal web page with a focus on cross-browser compatibility.
    \\ \emph{Technologies: HTML5, CSS3, jQuery}}
  \entry
    {2014}
    {Internet of Things Framework}
    {\href{http://git.io/vvL7B}{git.io/vvL7B}}
    {Developed a computational engine for the Internet of Things in collaboration with Ericsson and 
    the Swedish Institute of Computer Science (SICS) in the scope of the Project CS course 
    given at Uppsala University. 
    \\ \emph{Technologies: Ruby on Rails, Erlang, R, Elasticsearch}}
\end{entrylist}

\end{document}
